The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-15 document/ms.tex
words about RV follow-up

A study of the population of long-period transiting planets complements
parallel radial velocity \citep[RV; for example][]{Cumming:2008,
Knutson:2014, Bryan:2016}, microlensing \citep[for
example][]{Gould:2010, Cassan:2012, Clanton:2014, Shvartzvald:2016}, and
direct imaging \citep[for example][]{Bowler:2016}.
Exoplanets with both mass and radius measurements can be used to study
planetary compositions and the formation of planetary systems \citep[for
example][]{Weiss:2014, Rogers:2015, Wolfgang:2016}.
The existing catalog of exoplanets with measured densities is sparsely
populated at long orbital periods and discoveries with the transit method are
compelling targets for follow-up observations.
Furthermore, even at long orbital periods, the \kepler\ light curves should be
sensitive to smaller planets than the current state-of-the-art RV surveys.

@@

A real concern about the detection of exoplanets from a single transit is that
follow-up and confirmation is difficult.
Since the period of the orbit is poorly constrained and transits are sparse,
any prediction of a subsequent transit time will be too uncertain to schedule
targeted photometric follow-up.
Instead, follow-up using radial velocity and astrometry are more promising.

>>>>

A study of the population of long-period transiting planets complements
parallel radial velocity \citep[for example][]{Cumming:2008,
Knutson:2014, Bryan:2016}, microlensing \citep[for
example][]{Gould:2010, Cassan:2012, Clanton:2014, Shvartzvald:2016}, and
direct imaging \citep[for example][]{Bowler:2016}.
Exoplanets with both mass and radius measurements can be used to study
planetary compositions and the formation of planetary systems \citep[for
example][]{Weiss:2014, Rogers:2015, Wolfgang:2016}.
The existing catalog of exoplanets with measured densities is sparsely
populated at long orbital periods and discoveries with the transit method are
compelling targets for follow-up observations.
Furthermore, even at long orbital periods, the \kepler\ light curves should be
sensitive to smaller planets than the current state-of-the-art radial velocity
surveys.

@@

A real concern about the detection of exoplanets from a single transit is that
follow-up and confirmation is difficult.
Since the period of the orbit is poorly constrained and transits are sparse,
any prediction of a subsequent transit time will be too uncertain to schedule
targeted photometric follow-up.
Instead, follow-up using radial velocity and astrometry are more promising.
For both radial velocity and astrometry, there is information about the
orbiting planets in measurements made at all times~--~not just during transit.
This allows observations to be scheduled without a well constrained orbital
period.
Furthermore, follow-up of any of these candidates using radial velocity or
astrometry would provide a measurement of the density of a planet that would
be invaluable for the study of planetary compositions.

Table~\ref{tab:masses} lists the posterior predictions for the semi-amplitude
$K$ of the radial velocity signal produced by each candidate using the mass
predictions from the previous section.
Since the orbital periods are long, we also include a simple prediction for
the slope of the radial velocity trend induced by this planet by taking the
ratio of the semi-amplitude and the orbital period.
Any radial velocity follow-up of the candidates presented here would be an
ambitious undertaking because the stars are relatively faint and, in most
cases, the radial velocity trends are small.
Some candidates should, however, be within the reach of current
state-of-the-art facilities.
